Last glacial cycle glacier erosion potential in the Alps

### 2021-01-28 articles/erosion/alps-erosion.tex
Rework the climate sensitivity discussion.

    \note{I have not yet reworked the discussion.}

@@

    \note{I feel there is not much to learn from this section. I am thinking
          about just leaving it out.}

    The modelled erosion potential depends significantly on the choice of
    paleoclimate forcing applied, but the general patterns remain similar.
    Higher precipitation yields higher erosion. The results also appear to be
    sensitive to model resolution, primarily in the mountains interior, where
    bedrock slopes and sling speed depend more strongly on the grid size
    (Fig.~\ref{fig:sensitivity}).

>>>>

@@

    Different paleoclimate forcing scenarios lead to different modelled
    glaciation histories and thus different results in terms of erosion
    potential (Fig.~\ref{fig:sensitivity}). Scenarios including higher
    (constant) input precipitation rates yield generally higher modelled
    erosion potential (Fig.~\ref{fig:sensitivity}a, b, and~c), while scenarios
    including paleo-precipitation reductions (Fig.~\ref{fig:sensitivity}d, e,
    and~f), including our default high-resolution run, yield a smaller erosion
    potential. The spatial pattern of modelled erosion potential is
    nevertheless generally consistent across paleoclimate scenarios tested,
    despite variations in the glaciation maximum extent
    (Fig.~\ref{fig:sensitivity}). Furthermore, these changes are minor
    considering the large uncertainties affecting the choice of erosion law.
